Blocking-resistant communication\\through domain fronting

### 2014-07-30 docs/meek.tex
Don't confuse CloudFlare and CloudFront.

Amazon CloudFront (\url{https://aws.amazon.com/cloudfront/}),
not to be confused with CloudFlare,
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
a randomly generated subdomain of \urll{cloudflare.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other randomly generated subdomain---all
of which support HTTPS through a wildcard certificate---or
certain domain aliases like \urll{a0.awsstatic.com}.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50 gigabytes per month.

>>>>

Amazon CloudFront (\url{https://aws.amazon.com/cloudfront/}),
not to be confused with CloudFlare,
is the CDN of Amazon Web Services.
A CloudFront ``distribution'' associates
a randomly generated subdomain of \urll{cloudfront.net}
with an origin server,
which in our case is an instance of \meekserver.
The front domain may be any other randomly generated subdomain---all
of which support HTTPS through a wildcard certificate---or
certain domain aliases like \urll{a0.awsstatic.com}.
CloudFront has a usage tier that is free of charge for a year,
subject to a bandwidth limit of 50 gigabytes per month.
